---
title: "R Notebook"
output:
  word_document: default
  html_notebook: default
  pdf_document: default
---


```{r}
library(tidyverse)

data <- read_csv("Data/please1.csv")
auditData <- read_csv("Data/auditData.csv")

```

Get the top 50 most tenured names, removing duplicate names and the names of retired/problem directors that need to be cleaned out

Get the top 75 with duplicates

Get only the list of duplicates

```{r}

data <- data %>%
  mutate(YearsOnBoard = as.numeric(as.character(YearsOnBoard)))

DirectorList <- data %>%
  arrange(desc(YearsOnBoard)) %>%
  distinct(Name, .keep_all = TRUE) %>%
  filter(!Name %in% c("Howard J. Johnson", "M. Yaqub Mirza , PhD", "Edward I. Altman", "Kenneth A. Himmel", "Joni Evans")) %>%
  slice_head(n = 50)

# DirectorList <- data %>%
#   arrange(desc(YearsOnBoard)) %>%
#   distinct(Name, .keep_all = TRUE) %>%
#   slice_head(n = 50)

# DirectorList <- DirectorList %>% select(-DirectorId, -ComplexId, -FundBoardId, -blank, -blankik)


withDuplicates <- data %>%
  arrange(desc(YearsOnBoard)) %>%
  slice_head(n = 75)

onlyDuplicates <- withDuplicates %>% 
  group_by(Name) %>%
  filter(n() > 1) %>%
  ungroup()

```

Get gender breakdown in the top 50
Obtain average age of the top 50

```{r}
GenderBreakdown <- DirectorList %>% count(Gender)
AvgAge <- DirectorList %>% summarise(mean(`Age_As_ Of_Dec_31_2024`, na.rm = TRUE))
AvgTenure <- DirectorList %>% summarise(mean(`YearsOnBoard`, na.rm = TRUE))
FundGroups <- DirectorList %>%  arrange(desc(FundBoard)) %>% group_by(FundBoard)
AvgTenureAll <- data %>% summarise(mean(`YearsOnBoard`, na.rm = TRUE))

```

Creates list of everyone affiliated with a committee and then a breakdown of each in a table. Also does the same for the chairs/board positions
```{r}

ChairofBoard <- DirectorList %>% filter(!is.na(Position_With_Fund) & Position_With_Fund !="")
ChairTable <- DirectorList %>%  count(Position_With_Fund)
  
AuditCommittee <- DirectorList %>% filter(!is.na(Audit_Committee) & Audit_Committee != "")
AuditTable  <- DirectorList %>% count(Audit_Committee)
# AuditCommittee <- AuditCommittee %>% slice(-34)

NGCommittee <- DirectorList %>%  filter(!is.na(Nominating_Governance_Committee) & Nominating_Governance_Committee != "")
NGTable <- DirectorList %>% count(Nominating_Governance_Committee)

ContractCommittee <- DirectorList %>%  filter(!is.na(Contract_Committee) & Contract_Committee != "")
ContractTable <- DirectorList %>% count(Contract_Committee)

```


```{r}


dataFundClean <- data %>%
  mutate(FundBoard = if_else(str_detect(FundBoard, 
    "Franklin Templeton|Putnam|Royce|Martin Currie|Western Asset|Lexington|Clarion|Clearbridge|Brandywine"),
    "Franklin Templeton ADJ", FundBoard))

dataFundClean <- data %>%
  mutate(FundBoard = if_else(str_detect(FundBoard, 
    "BNY"),"BNY ADJ", FundBoard))

dataFundClean <- dataFundClean %>%
  mutate(YearsOnBoard = as.numeric(as.character(YearsOnBoard)))


FundTenure <- dataFundClean %>% group_by(FundBoard) %>% summarise(AvgYearsOnBoard = mean(YearsOnBoard, na.rm = TRUE))


```